Should geophysicists use the gravity disturbance or the anomaly?

### 2018-06-20 manuscript/letter.tex
two-column and manuscript versions

\documentclass[paper,twocolumn,twoside]{geophysics}
%\documentclass[manuscript,revised]{geophysics}

@@

%\plot{cartesian-geodetic-systems}{width=0.6\textwidth}{
\plot{cartesian-geodetic-systems}{width=\columnwidth}{
	{(a) and (b) The Geocentric Cartesian System (GCS) and the Geocentric
		Geodetic System (GGS).
		The GGS is defined by an oblate ellipsoid with semi-minor axis $b$ and
		semi-major axis $a$.
		In this coordinate system, the position of a point is determined by the
		geometric height $h$, geodetic latitude $\varphi$, and longitude $\lambda$.
		$O$ is the Earth's center of mass, $P$ is an observation point, and
		unit vectors $\mathbf{u}$, $\mathbf{v}$, and $\mathbf{w}$ define mutually
		orthogonal directions at $P$ (equation \ref{eq:unit-vectors}).
		In (b), $Q$ is the projection of $P$ onto the reference ellipsoid at
		the same latitude and longitude.
		(c) The topocentric Cartesian coordinate system (TCS) with origin at a
		point $P$.
		Axes $x$ and $y$ are parallel to the unit vectors $\mathbf{v}$ and
		$\mathbf{w}$, respectively, and the $z$ axis is opposite to $\mathbf{u}$.
		The gray plane is the same shown in (a) and (b).}
	\label{fig:systems}
}

%\plot{surfaces}{width=0.6\textwidth}{
\plot{surfaces}{width=\columnwidth}{
	{The gravity vector
		$\mathbf{g}_{P}$, normal gravity vector $\boldsymbol{\gamma}_{P}$,
		gravity disturbance vector $\delta \mathbf{g}_{P}$
		(equation \ref{eq:gravity-disturbance-vector}), and unit vector
		$\mathbf{u}_{P}$ (equation \ref{eq:unit-vectors}) at a point $P$ 
		on the surface of the Earth.
		The gravity vector $\mathbf{g}_{Q^{\prime}}$
		at a point $Q^{\prime}$ on the geoid, normal gravity vector
		$\boldsymbol{\gamma}_{Q}$ at a point $Q$ on the reference ellipsoid,
		geometric height $h$, orthometric height $H$, and geoidal height $N$.
		The dashed line passing through
		$Q$, $Q^{\prime}$ and $P$ is normal to the
		surface of the reference ellipsoid at $Q$.
		This figure shows a commonly used approximation in which the ellipsoid and
		geoid are represented as parallel surfaces so that $h \approx H + N$.} 
	\label{fig:surfaces}
}

%\plot{difference}{width=0.6\textwidth}{
\plot{difference}{width=\columnwidth}{
	{Absolute difference between the gravity disturbance and free-air anomaly.
		Calculated using equation \ref{eq:difference-disturbance-free-air}, the
		EIGEN-6c4 \citep{forste2014} spherical harmonic model, and software
		\textit{Fatiando a Terra} \citep{uieda2013}. The figure was made using GMT
		\citep{wessel2013}.}
	\label{fig:difference}
}

>>>>

%\documentclass[paper,twocolumn,twoside]{geophysics}
%\documentclass[manuscript,revised]{geophysics}
\documentclass[manuscript]{geophysics}

@@

\plot{cartesian-geodetic-systems}{width=0.6\textwidth}{
%\plot{cartesian-geodetic-systems}{width=\columnwidth}{
	{(a) and (b) The Geocentric Cartesian System (GCS) and the Geocentric
		Geodetic System (GGS).
		The GGS is defined by an oblate ellipsoid with semi-minor axis $b$ and
		semi-major axis $a$.
		In this coordinate system, the position of a point is determined by the
		geometric height $h$, geodetic latitude $\varphi$, and longitude $\lambda$.
		$O$ is the Earth's center of mass, $P$ is an observation point, and
		unit vectors $\mathbf{u}$, $\mathbf{v}$, and $\mathbf{w}$ define mutually
		orthogonal directions at $P$ (equation \ref{eq:unit-vectors}).
		In (b), $Q$ is the projection of $P$ onto the reference ellipsoid at
		the same latitude and longitude.
		(c) The topocentric Cartesian coordinate system (TCS) with origin at a
		point $P$.
		Axes $x$ and $y$ are parallel to the unit vectors $\mathbf{v}$ and
		$\mathbf{w}$, respectively, and the $z$ axis is opposite to $\mathbf{u}$.
		The gray plane is the same shown in (a) and (b).}
	\label{fig:systems}
}

\plot{surfaces}{width=0.6\textwidth}{
%\plot{surfaces}{width=\columnwidth}{
	{The gravity vector
		$\mathbf{g}_{P}$, normal gravity vector $\boldsymbol{\gamma}_{P}$,
		gravity disturbance vector $\delta \mathbf{g}_{P}$
		(equation \ref{eq:gravity-disturbance-vector}), and unit vector
		$\mathbf{u}_{P}$ (equation \ref{eq:unit-vectors}) at a point $P$ 
		on the surface of the Earth.
		The gravity vector $\mathbf{g}_{Q^{\prime}}$
		at a point $Q^{\prime}$ on the geoid, normal gravity vector
		$\boldsymbol{\gamma}_{Q}$ at a point $Q$ on the reference ellipsoid,
		geometric height $h$, orthometric height $H$, and geoidal height $N$.
		The dashed line passing through
		$Q$, $Q^{\prime}$ and $P$ is normal to the
		surface of the reference ellipsoid at $Q$.
		This figure shows a commonly used approximation in which the ellipsoid and
		geoid are represented as parallel surfaces so that $h \approx H + N$.} 
	\label{fig:surfaces}
}

\plot{difference}{width=0.6\textwidth}{
%\plot{difference}{width=\columnwidth}{
	{Absolute difference between the gravity disturbance and free-air anomaly.
		Calculated using equation \ref{eq:difference-disturbance-free-air}, the
		EIGEN-6c4 \citep{forste2014} spherical harmonic model, and software
		\textit{Fatiando a Terra} \citep{uieda2013}. The figure was made using GMT
		\citep{wessel2013}.}
	\label{fig:difference}
}
